Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-23 ICML2019/main.tex
Finished pass on section 4.

\section{Problem Statement}
\label{subsec_problem}
We are interested in exploring the design space of mechanisms for privately releasing the posterior
distribution for the Dirichlet-Multinomial model by output
perturbation with accuracy measured in Hellinger distance.
It is worth noticing that the posterior distribution of this model is fully characterized
by its parameters. That is, we are interested in releasing a private version of
the Dirichlet distribution with parameter
$\valpha'=(\valpha + \Delta \valpha)$, where $\valpha$ is the
parameter of the prior, and $\Delta \valpha$ is computed from the data
as discussed in the previous section. In the case of the
Beta-Binomial model this specialize to releasing a private version of the Beta distribution with 
parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n -
\Delta \alpha)$, where $\alpha$ and $\beta$ are the parameters of the
prior, and $\Delta \alpha$ is the number of $1$ in the data.

Previous work by \citet{zhang2016differential} and \citet{xiao2012bayesian}
have considered the problem of releasing the posterior of the
Beta-Binomial model by output perturbation with accuracy measured in terms of
$\ell_1$ norm. In addition,   \citet{zhang2016differential} has also
considered KL-divergence between posteriors. 
In this work we consider instead the Hellinger Distance between
posteriors. Similarly to KL-divergence, Hellinger Distance is an
$f$-divergence measuring levels of similarities between
distributions. However, unlikely KL-divergence, Hellinger Distance is a proper
distance satisfying reflexivity, symmetry and triangle
inequality. These properties gives Hellinger Distance analytical
advantages and makes the minimum hellinger distance  an efficient and
robust estimator~\cite{}.

attacked this problem by adding independent Laplacian noise to the
parameters of the posteriors. That is, in the case of the Beta-Binomial system,
the values released would be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
where $\widetilde{\Delta \alpha}\thicksim \lap{\Delta \alpha}{\frac{2}{\epsilon}}$,
and where $\lap{\mu}{\nu}$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t. to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent data observations $\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Section \ref{sec_mechs}.\\
However, in previous works, the accuracy of the posterior was measured with respect to $\ell_1$ norm. That is, an upper bound was given on
\[
  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
\]
where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are the real and the perturbed pairs of parameters, respectively.
However, distance between
distributions are more naturally  measured by distribution
metrics such as $f$-divergences, e.g. Hellinger distance, etc., than the $\ell_1$ norm shown above.
{\color{blue} still not sure this is a good way to put it...}
This gives us motivation for exploring the design space
of mechanisms by considering different norms. e.g. a norm over space of measures.
to compute the sensitivity and provide guarantees on the accuracy.

\begin{figure}[ht]
\centering
\includegraphics[width=0.32\textwidth]{sensitivity_2d.eps}
\caption{Local sensitivity of $\hellinger$. Data size is 100. $\alpha$ is the number of 1s.}
\label{fig_sensitivity}
\end{figure}

>>>>

\section{Problem Statement}
\label{subsec_problem}
We are interested in exploring the design space of mechanisms for privately releasing the posterior
distribution for the Dirichlet-Multinomial model by output
perturbation with accuracy measured in Hellinger distance. We assume
that the prior is given and non-private and we aim at protecting the
privacy of the observed data.
It is worth noticing that the posterior distribution of the Dirichlet-Multinomial model is fully characterized
by its parameters. That is, we are interested in releasing a private version of
the Dirichlet distribution with parameter
$\valpha'=(\valpha + \Delta \valpha)$, where $\valpha$ is the
parameter of the prior, and $\Delta \valpha$ is computed from the data
as discussed in the previous section. In the case of the
Beta-Binomial model this specialize to releasing a private version of the Beta distribution with 
parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n -
\Delta \alpha)$, where $\alpha$ and $\beta$ are the parameters of the
prior, and $\Delta \alpha$ is the number of $1$ in the data.

Previous work by \citet{zhang2016differential} and \citet{xiao2012bayesian}
have considered the problem of releasing the posterior of the
Beta-Binomial model by output perturbation with accuracy measured in terms of
$\ell_1$ norm. In addition,  \citet{zhang2016differential} has also
considered KL-divergence between posteriors. 
In this work we consider instead the Hellinger distance between
posteriors. Similarly to KL-divergence, Hellinger distance is an
$f$-divergence measuring levels of similarities between
distributions. However, unlikely KL-divergence, Hellinger distance is a proper
distance satisfying reflexivity, symmetry and triangle
inequality. These properties gives Hellinger distance analytical
advantages and makes the minimum hellinger distance  an efficient and
robust estimator~\cite{}.

% attacked this problem by adding independent Laplacian noise to the
% parameters of the posteriors. That is, in the case of the Beta-Binomial system,
% the values released would be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
% where $\widetilde{\Delta \alpha}\thicksim \lap{\Delta \alpha}{\frac{2}{\epsilon}}$,
% and where $\lap{\mu}{\nu}$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
% This mechanism is $\epsilon$-differentially private, and the noise is
% calibrated w.r.t. to a sensitivity of 2 which is derived by using
% $\ell_1$ norm over the pair of parameters. Indeed, considering two
% adjacent data observations $\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
% distributions, characterized by the pairs
% $(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
% $|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
% This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Section \ref{sec_mechs}.\\
% However, in previous works, the accuracy of the posterior was measured with respect to $\ell_1$ norm. That is, an upper bound was given on
% \[
%   \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
% \]
% where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are the real and the perturbed pairs of parameters, respectively.
% However, distance between
% distributions are more naturally  measured by distribution
% metrics such as $f$-divergences, e.g. Hellinger distance, etc., than the $\ell_1$ norm shown above.
% {\color{blue} still not sure this is a good way to put it...}
% This gives us motivation for exploring the design space
% of mechanisms by considering different norms. e.g. a norm over space of measures.
% to compute the sensitivity and provide guarantees on the accuracy.

One of the challenges in working with the Hellinger distance for the
Dirichlet-multinomial model is that a difference in the parameters of two
Dirichlet distributions can results in different values  in terms of Hellinger distance
depending on the value of the parameter
themselves. The plot in Figure~\ref{fig_sensitivity} illustrates
this by showing the Hellinger distance between beta distributions
whose parameters differ by one, for each value of the parameter
$\alpha$. The reason why this change is relevant
for differential privacy is that this quantity corresponds to the local
sensitivity of the function $\hellinger$.

\begin{figure}[ht]
\centering
\includegraphics[width=0.32\textwidth]{sensitivity_2d.eps}
\caption{Hellinger distance between the Beta distributions
  corresponding to two adjacent datasets of size 100
  when  $\alpha$ (the number of 1s) changes. This quantity corresponds
  to the local sensitivity of the function $\hellinger$.}
\label{fig_sensitivity}
\end{figure}
